---
title: "Regression Examples"
date: "`r Sys.Date()`"
author: "Harm"
output:
  rmdformats::robobook:
    highlight: kate
---

*This code is mostly taken from the intro to the fabulous [fixest package](https://cran.r-project.org/web/packages/fixest/index.html)*

## Setup

```{r setup}
library(tidyverse)
library(haven)  # for reading/writing stata, spss, and sas files
library(fixest)  # fixed effects, clustered SE, and IV regressions
```

## Data

```{r}
trade <- read_dta("../data/trade.dta")
glimpse(trade)
```

```{r}
head(trade)
```


## An example model with fixed effects

The dependent variable of the estimation will be the level of trade between two countries while the independent variable is the geographic distance between the two countries. To obtain the elasticity of geographic distance net of the effects of the four fixed-effects, we estimate the following:

$$E\left(Trade_{i,j,p,t}\right)=\gamma_{i}^{Exporter}\times\gamma_{j}^{Importer}\times\gamma_{p}^{Product}\times\gamma_{t}^{Year}\times Distance_{ij}^{\beta}$$

In log form this is: 

$$E\left(Trade_{i,j,p,t}\right)=\exp\left(\gamma_{i}^{Exporter}+\gamma_{j}^{Importer}+\gamma_{p}^{Product}+\gamma_{t}^{Year}+\beta\times \ln Distance_{ij}\right)$$

## Regression examples

This is how we can estimate the model in linear form:

```{r}
m1 <- feols(log(Euros) ~ log(dist_km) | Origin + Destination + Product + Year, data = trade)
summary(m1, vcov = ~ Origin + Year)
```

```{r}
m2 <- feols(
  log(Euros) ~ log(dist_km) | Origin + Destination + Product + Year, 
  data = trade,
  vcov = ~Origin + Destination
  )
```


```{r}
etable(m1, m2) 
```

```{r}
model_list <- list()
all_FEs  <- c("Year", "Destination", "Origin")
for (i in 0:3){
  model_list[[i+1]] <- feols(log(Euros) ~ log(dist_km),
                             data = trade,
                             fixef = all_FEs[0:i])
}
etable(model_list, cluster =  ~Origin + Destination)
```



## Nesting and Regressions

```{r}
fit_model <- function(dta) {
  fit <- feols(
    log(Euros) ~ log(dist_km) | Origin + Destination + Product, 
    data = dta
    )
  return(fit)
}

nested_by_year <- 
  trade |> 
  nest(data = -Year) |> 
  mutate(fit = map(data, fit_model)) |> 
  mutate(preds = map2(fit, data, \(x, y) predict(x, y)))
```

```{r}
head(nested_by_year)
```


```{r}
nested_by_year$fit[[2]]
```

```{r}
fitted_trade <- 
  nested_by_year |> 
  select(-fit) |> 
  unnest(c(data, preds)) |> 
  mutate(predicted_Euros = exp(preds))

head(fitted_trade)
```
